---
title: "Untitled"
author: "Jiaxin Li"
date: "2023-12-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gridExtra)
library(knitr)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(tidyverse)
library(stringr)
library(openxlsx)


```



```{r}
sey <- read.xlsx("sey_data.xlsx")
transposed_data <- t(sey)


transposed_df <- as.data.frame(transposed_data)


colnames(transposed_df) <- transposed_df[1, ]


transposed_df <- transposed_df[-1, ]


transposed_df <- transposed_df %>%
  mutate_all(as.numeric)

sey_df <- transposed_df %>%
  mutate(year = rownames(transposed_df))
sey_df$year <- as.numeric(as.character(sey_df$year))

# View(sey_df)

naomit <- na.omit(sey_df[, c("year", "migrant_popu_proportion")])
naomit2 <- na.omit(sey_df[, c("year", "Human_capital_index_upper_bound")])
naomit3 <- na.omit(sey_df[, c("year", "GDP")])
naomit4 <- na.omit(sey_df[, c("year", "GDP_growth_annual")])

```



```{r}
Seychelles <- read.xlsx("Seychelles.xlsx")
```



```{r}
adjusted_net_national_income_per_capita_Usdollar <- ggplot(data = Seychelles, aes(x = year, y = adjusted_net_national_income_per_capita_Usdollar)) +
  geom_line(aes(group = 1), color = "purple") + 
  geom_point(aes(color = "pink")) +
  labs(
    title = "The annual changes in the adjusted net national income per capita (US$)",
    x = "Year",
    y = "Adjusted Net National Income Per Capita (US$))"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))

```



```{r}
export_value_index <- ggplot(data = Seychelles, aes(x = year, y = export_value_index)) +
  geom_line(aes(group = 1), color = "purple") + 
  geom_point(aes(color = "pink")) +
  labs(
    title = "The annual changes in the export value index (2015=100)",
    x = "Year",
    y = "Export Value Index"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))



import_value_index <- ggplot(data = Seychelles, aes(x = year, y = import_value_index)) +
  geom_line(aes(group = 1), color = "purple") + 
  geom_point(aes(color = "pink")) +
  labs(
    title = "The annual changes in the import value index (2015=100)",
    x = "Year",
    y = "Import Value Index"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))



```











```{r}
total_population_change <- ggplot(data = sey_df, aes(x = year, y = population)) +
  geom_line(aes(group = 1), color = "blue") +  
  geom_point(aes(color = "pink")) +
  labs(
    title = "The total population in Seychelles",
    x = "Year",
    y = "Total Population"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))







female_percentage_of_population_change <- ggplot(data = sey_df, aes(x = year, y = female_percentage)) +
  geom_line(aes(group = 1), color = "blue") + 
  geom_point(aes(color = "pink")) +
  labs(
    title = "The annual changes in the proportion of females in the total population",
    x = "Year",
    y = "Proportion of Females (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)) +
  geom_hline(yintercept = 50, linetype = "dashed", color = "red")

female_percentage_of_population_change





old_popu_proportion <- ggplot(data = sey_df, aes(x = year, y = old_popu_proportion)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") + 
  labs(
    title = "The changing trend of population aging over the years",
    x = "Year",
    y = "Proportion of the Population Aged 65 and Above"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))

old_popu_proportion





migrant_popu_proportion <- ggplot(data = naomit, aes(x = year, y = migrant_popu_proportion)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") +  
  labs(
    title = "The changes in the proportion of migrants",
    x = "Year",
    y = "Proportion of the Migrants (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))

migrant_popu_proportion





HCI <- ggplot(data = naomit2, aes(x = year, y = Human_capital_index_upper_bound)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") +  
  labs(
    title = "The changes in the level of human capital development from 2010",
    x = "Year",
    y = "Human Capital Index (upper bound)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))

HCI






inflation <- ggplot(data = sey_df, aes(x = year, y = Consumer_price_index)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") +  
  labs(
    title = "The changes in the level of inflation over years",
    x = "Year",
    y = "Consumer Price Index"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))
inflation

```














```{r}
exports_of_goods_and_services <- ggplot(data = sey_df, aes(x = year, y = exports_of_goods_and_services)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "lightblue") +  
  labs(
    title = "The annual changes in the exports of goods and services",
    x = "Year",
    y = "Exports of Goods and Services"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))
exports_of_goods_and_services




imports_of_goods_and_services <- ggplot(data = sey_df, aes(x = year, y = imports_of_goods_and_services)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the imports of goods and services",
    x = "Year",
    y = "Imports of Goods and Services"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))
imports_of_goods_and_services
```










```{r}
young_percentage_of_working_age_popu <- ggplot(data = sey_df, aes(x = year, y = young_percentage_of_working_age_popu)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "lightblue") + 
  labs(
    title = "The annual changes in the proportion of young laborers within the total labor force",
    x = "Year",
    y = "Proportion of Young Laborers (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))



old_percentage_of_working_age_popu <- ggplot(data = sey_df, aes(x = year, y = old_percentage_of_working_age_popu)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "lightblue") + 
  labs(
    title = "The annual changes in the proportion of old laborers within the total labor force",
    x = "Year",
    y = "Proportion of Old Laborers (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))




unemployment_prop <- ggplot(data = sey_df, aes(x = year, y = unemployment_prop)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the proportion of unemployment population",
    x = "Year",
    y = "Proportion of Unemployment Population (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))

```






















```{r}
GDP <- ggplot(data = naomit3, aes(x = year, y = GDP)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") +  
  labs(
    title = "The value of GDP over years",
    x = "Year",
    y = "GDP"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))



GDP_growth_annual <- ggplot(data = naomit4, aes(x = year, y = GDP_growth_annual)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") +  
  labs(
    title = "The GDP annual growth over years",
    x = "Year",
    y = "GDP Annual Growth (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "red")



```







## Population
The Seychelles has a population of approximately 90,000 people who mostly live on eight of the Seychelles' 115 islands. 90% of the population live on the main island of Mahé. The next-largest populations are on Praslin and La Digue respectively. In total, eight of the Seychelles' islands are permanently inhabited.

The Seychelles have attracted people from all over the world. The multi-ethnic roots of the Seychelles people stretch far and wide, including France, India, the UK, China, the Arab world, and other parts of Africa.

There are three official languages in the Seychelles: Creole, English, and French. The most common language spoken by the Seychellois population is their own Creole variant, Seychellois Creole, or Seselwa. This language is a mix of African languages such as Swahili and Malagasy, but with large French influences.







## climate

Seychelles has a tropical climate with high humidity. Temperatures don’t fluctuate much throughout the year. Afternoons are around 30°C/86°F and nights are cooler at around 24°C/75°F. It rains throughout the year; December and January are the wettest months. The hottest, most humid months are December to April.

1. Dry Season (May to September)
This period is drier, but it can still rain at any time. It is also cooler and the humidity is lower. This is the most pleasant time of the year, but the southeast monsoon can bring strong winds at sea.
(1) May: It cools down slightly and rainfall decreases.
(2) June, July and August: These are the coolest months and the chance of rain is less. The average temperature in the afternoon is 29°C/84°F.
(3) September: Temperatures start to pick up again and so does the chance of rain.

2. Wet Season(October to April)
November to April sees a lot of rain and this peaks from mid-December to the end of January. Humidity is at its highest in March and April.
(1) October and November: These months see a fair bit of rain and the humidity increases.
(2) December, January and February: It is very hot and humid. Big showers and storms are common.
(3) March and April: These are the hottest months and the humidity can be hard to bear. The afternoon temperature averages at 31°C/88°F and rainfall diminishes slightly.



## Best Time to Visit







## Popular destinations

Seychelles is a popular beach destination, both in its own right and as an add-on to an African safari. All international flights arrive at Seychelles International Airport (SEZ), 8km/5mi south of Victoria on Mahé. 

Entry Requirements：
(1) A passport is required for all foreign visitors and has to be valid for the period of the intended stay until arrival back in the country of residence.
(2) Regardless of nationality, a free visitor's permit valid for up to one month is issued on arrival.
(3) Permits can be extended free of charge for up to three months.

The main attractions in Seychelles are its three main islands. Additionally, one might consider day trips to some of the smaller islands：

1.Main islands:
(1) Mahé for experiencing the hustle and bustle of Victoria, walking in Morne Seychellois National Park and some beach time at Beau Vallon
(2) Praslin for seeing coco de mer palms at Vallée de Mai, snorkeling at Ile Cocos and sunbathing on Anse Lazio
(3) La Digue for spending time on picture-perfect beaches Anse Source d’Argent and Grand Anse

2. Popular add-ons:
(1) Bird Island for seeing colonies of sooty terns and nesting turtles
(2) Cousin Island for spotting Seychelles warblers and other endemic birds
(3) Curieuse Island for walking along coastal trails and seeing giant tortoises















The indicator "Food production index (2014-2016 = 100)" refers to the Food Production Index, with the base set at 100 using the average values from 2014 to 2016. The purpose of this index is to measure the changes in food production for a specific region or country relative to the baseline period (2014-2016). If the index value is 100, it indicates that the food production is the same as the baseline period. A value above 100 suggests an increase in food production, while a value below 100 indicates a decrease. Such indices are commonly used to assess trends in food security and food production.
```{r}

```








```{r}
library(shiny)
library(ggplot2)

# Assuming your data is already loaded and named sey_df, naomit, naomit2, naomit3, naomit4
# If not, load your data here

# Define UI
ui <- fluidPage(
  titlePanel("Seychelles"),

  tabsetPanel(
    tabPanel("Population Overview",
             fluidPage(
               sliderInput("year_range_pop", "Select Year Range", min = 1960, max = 2022, value = c(1960, 2022), step = 1),
               actionButton("btn_total_population_change", "Total Population Change"),
               actionButton("btn_female_percentage", "Female Percentage"),
               actionButton("btn_old_popu_proportion", "Old Population Proportion"),
               actionButton("btn_migrant_popu_proportion", "Migrant Population Proportion"),
               plotOutput("plot_pop")
             )
    ),

    tabPanel("Economic Overview",
             fluidPage(
               sliderInput("year_range_eco", "Select Year Range", min = 1960, max = 2022, value = c(1960, 2022), step = 1),
               actionButton("btn_GDP", "GDP"),
               actionButton("btn_GDP_growth_annual", "GDP Growth Annual"),
               actionButton("btn_imports_of_goods_and_services", "Imports of Goods and Services"),
               actionButton("btn_exports_of_goods_and_services", "Exports of Goods and Services"),
               actionButton("btn_inflation", "Inflation"),
               actionButton("btn_HCI", "Human Capital Index"),
               plotOutput("plot_eco")
             )
    ),

    tabPanel("Employment Overview",
             fluidPage(
               sliderInput("year_range_emp", "Select Year Range", min = 1960, max = 2022, value = c(1960, 2022), step = 1),
               actionButton("btn_young_percentage_of_working_age_popu", "Young Percentage of Working Age Population"),
               actionButton("btn_old_percentage_of_working_age_popu", "Old Percentage of Working Age Population"),
               actionButton("btn_unemployment_prop", "Unemployment Proportion"),
               plotOutput("plot_emp")
             )
    )
  )
)

# Define Server
server <- function(input, output) {
  current_plot_pop <- reactiveVal(NULL)
  current_plot_eco <- reactiveVal(NULL)
  current_plot_emp <- reactiveVal(NULL)

  observeEvent(input$btn_total_population_change, {
    current_plot_pop(total_population_change +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_pop))
  })

  observeEvent(input$btn_female_percentage, {
    current_plot_pop(female_percentage_of_population_change +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_pop))
  })

  observeEvent(input$btn_old_popu_proportion, {
    current_plot_pop(old_popu_proportion +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_pop))
  })

  observeEvent(input$btn_migrant_popu_proportion, {
    current_plot_pop(migrant_popu_proportion +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_pop))
  })

  observeEvent(input$btn_GDP, {
    current_plot_eco(GDP +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_eco))
  })

  observeEvent(input$btn_GDP_growth_annual, {
    current_plot_eco(GDP_growth_annual +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_eco))
  })

  observeEvent(input$btn_imports_of_goods_and_services, {
    current_plot_eco(imports_of_goods_and_services +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_eco))
  })

  observeEvent(input$btn_exports_of_goods_and_services, {
    current_plot_eco(exports_of_goods_and_services +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_eco))
  })

  observeEvent(input$btn_inflation, {
    current_plot_eco(inflation +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_eco))
  })

  observeEvent(input$btn_HCI, {
    current_plot_eco(HCI +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_eco))
  })

  observeEvent(input$btn_young_percentage_of_working_age_popu, {
    current_plot_emp(young_percentage_of_working_age_popu +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_emp))
  })

  observeEvent(input$btn_old_percentage_of_working_age_popu, {
    current_plot_emp(old_percentage_of_working_age_popu +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_emp))
  })

  observeEvent(input$btn_unemployment_prop, {
    current_plot_emp(unemployment_prop +
                    scale_x_continuous(breaks = seq(1960, 2022, by = 5),
                                       limits = c(1960, 2022)) +
                    coord_cartesian(xlim = input$year_range_emp))
  })

  output$plot_pop <- renderPlot({
    print(current_plot_pop())
  })

  output$plot_eco <- renderPlot({
    print(current_plot_eco())
  })

  output$plot_emp <- renderPlot({
    print(current_plot_emp())
  })
}

shinyApp(ui, server)

```








```{r}
library(shiny)
library(leaflet)


ui <- fluidPage(
  titlePanel("Map of Seychelles"),

  mainPanel(
    leafletOutput("seychelles_map")
  )
)

server <- function(input, output) {

  output$seychelles_map <- renderLeaflet({
    leaflet() %>%
      setView(55.4760, -4.6600, zoom = 2) %>%  # 设置初始视图
      addTiles() %>%  # 添加地图瓦片
      addMarkers(lng = 55.4760, lat = -4.6600, popup = "Seychelles")  # 在地图上添加标记
  })
}

shinyApp(ui, server)
```



















```{r}
colnames(sey_df)
```



```{r}
individuals_using_the_Internet_proportion <- ggplot(data = sey_df, aes(x = year, y = individuals_using_the_Internet_proportion)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the individuals using the Internet proportion",
    x = "Year",
    y = "Proportion (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))







CO2_emissions_kt <- ggplot(data = sey_df, aes(x = year, y = CO2_emissions_kt)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the CO2 emissions(kt)",
    x = "Year",
    y = "CO2 Emissions (kt)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))





renewable_energy_consumption_proportion <- ggplot(data = sey_df, aes(x = year, y = renewable_energy_consumption_proportion)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the renewable energy consumption proportion",
    x = "Year",
    y = "Proportion (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))



access_to_electricity_proportion <- ggplot(data = sey_df, aes(x = year, y = access_to_electricity_proportion)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the access-to-electricity population proportion",
    x = "Year",
    y = "Proportion (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))











central_government_debt_billions <- ggplot(data = sey_df, aes(x = year, y = central_government_debt_billions)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "pink") +
  labs(
    title = "The annual changes in the central government debt (billions)",
    x = "Year",
    y = "Central Government Debt (billions)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))


expense_percentage_of_GDP <- ggplot(data = sey_df, aes(x = year, y = expense_percentage_of_GDP)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "pink") +
  labs(
    title = "The annual changes in the expense (% of GDP)",
    x = "Year",
    y = "Expense (% of GDP)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))




total_tax_revenue <- ggplot(data = sey_df, aes(x = year, y = total_tax_revenue)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "pink") +
  labs(
    title = "The annual changes in the total tax revenue",
    x = "Year",
    y = "Total Tax Revenue"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))




foreign_direct_investment_percentage_of_GDP <- ggplot(data = sey_df, aes(x = year, y = foreign_direct_investment_percentage_of_GDP)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "pink") +
  labs(
    title = "The annual changes in the foreign direct investment (% of GDP)",
    x = "Year",
    y = "Foreign Direct Investment (% of GDP)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))









```























```{r}
library(shiny)
library(leaflet)
library(ggplot2)


ui <- fluidPage(
  titlePanel("Exploring Seychelles: A Tropical Paradise Unveiled"),
  
  tabsetPanel(
    tabPanel("Seychelles",
             img(src = "sey photo1.png", height = 500, width = 800),
             img(src = "sey photo2.png", height = 500, width = 800)
    ),

    tabPanel("Where are Seychelles and Its Neighbors",
             fluidPage(
               leafletOutput("seychelles_map"),
               verbatimTextOutput("map_note")
             )
    ),

    tabPanel("Explore Seychelles",
             fluidPage(
               selectInput("section", "Population, Economy, Society and Environment", choices = c("Population", "Economy", "Society and Environment")),
               uiOutput("plot_selector"),
               plotOutput("selected_plot")
             )
    ),
    
    tabPanel("SWOT Analysis for Seychelles",
             fluidPage(
               tableOutput("swot_table")
             )
    ),
    
    tabPanel("Travel to Seychelles",
             fluidPage(
               tableOutput("Seychelles_visit")
             )
    ),
    
    tabPanel("Comparison Between Seychelles and Its Neighbors",
             fluidPage(
               tableOutput("country_comparison_table")
             )
    ),
    
    tabPanel("Main Data Origin",
             fluidPage(
               tableOutput("references_table"),
               verbatimTextOutput("data_origin_note")
             )
    )
  )
)





server <- function(input, output) {
  output$seychelles_map <- renderLeaflet({
    leaflet() %>%
      setView(-4.6796, 55.4920, zoom = 2) %>%  
      addTiles() %>%  
      addMarkers(lng = 55.4920, lat = -4.6796, popup = "Seychelles")%>%
      addMarkers(lng = 43.3333, lat = -11.6455, popup = "Neighbor1: Comoros") %>%
      addMarkers(lng = 57.5522, lat = -20.3484, popup = "Neighbor2: Mauritius") %>%
      addMarkers(lng = 55.5364, lat = -21.1151, popup = "Neighbor3: Reunion")
  })
  
  output$map_note <- renderPrint({
    cat("Seychelles is located in the Atlantic, Indian Ocean, and South China Sea (AIS) (IOC) region. The main neighboring countries are Comoros, Mauritius, and Reunion. Please click on the markers to view the country names. Feel free to zoom in and explore the areas of interest.")
  })

  output$plot_selector <- renderUI({
    section <- input$section

    if (section == "Population") {
      choices <- c(
        "Total Population Change",
        "Female Percentage",
        "Old Population Proportion",
        "Migrant Population Proportion",
        "Human Capital Index"
      )
    } else if (section == "Economy") {
      choices <- c(
        "Adjusted Net National Income Per Capita (US$)",
        "GDP",
        "GDP Growth Annual",
        "central Government Debt",
        "Total Tax Revenue",
        "Consumer Price Index",
        "Export Value Index",
        "Import Value Index",
        "Exports of Goods and Services",
        "Imports of Goods and Services",
        "Foreign Direct Investment (% of GDP)"
      )
    } else if (section == "Society and Environment") {
      choices <- c(
        "CO2 Emissions",
        "Renewable Energy Consumption Proportion",
        "Individuals Access to Electricity Proportion",
        "Individuals Using the Internet Proportion",
        "Young Percentage of Working Age Population",
        "Old Percentage of Working Age Population",
        "Unemployment Proportion"
      )
    }

    selectInput("plot_selector", "Please choose the indicators that interest you", choices = choices)
  })

  selected_plot <- reactive({
    section <- input$section
    plot_selector <- input$plot_selector

    if (section == "Population") {
      switch(
        plot_selector,
        "Total Population Change" = ggplot(data = sey_df, aes(x = year, y = population)) +
  geom_line(aes(group = 1), color = "blue") +  
  geom_point(aes(color = "pink")) +
  labs(
    title = "The total population in Seychelles",
    x = "Year",
    y = "Total Population"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Female Percentage" = ggplot(data = sey_df, aes(x = year, y = female_percentage)) +
  geom_line(aes(group = 1), color = "blue") + 
  geom_point(aes(color = "pink")) +
  labs(
    title = "The annual changes in the proportion of females in the total population",
    x = "Year",
    y = "Proportion of Females (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)) +
  geom_hline(yintercept = 50, linetype = "dashed", color = "red"),
        "Old Population Proportion" = ggplot(data = sey_df, aes(x = year, y = old_popu_proportion)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") + 
  labs(
    title = "The changing trend of population aging over the years",
    x = "Year",
    y = "Proportion of the Population Aged 65 and Above"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Migrant Population Proportion" = ggplot(data = naomit, aes(x = year, y = migrant_popu_proportion)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") +  
  labs(
    title = "The changes in the proportion of migrants",
    x = "Year",
    y = "Proportion of the Migrants (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Human Capital Index" = ggplot(data = naomit2, aes(x = year, y = Human_capital_index_upper_bound)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") +  
  labs(
    title = "The changes in the level of human capital development from 2010",
    x = "Year",
    y = "Human Capital Index (upper bound)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))
      )
    } else if (section == "Economy") {
      switch(
        plot_selector,
        "Adjusted Net National Income Per Capita (US$)" = ggplot(data = Seychelles, aes(x = year, y = adjusted_net_national_income_per_capita_Usdollar)) +
  geom_line(aes(group = 1), color = "purple") + 
  geom_point(aes(color = "pink")) +
  labs(
    title = "The annual changes in the adjusted net national income per capita (US$)",
    x = "Year",
    y = "Adjusted Net National Income Per Capita (US$))"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "GDP" = ggplot(data = naomit3, aes(x = year, y = GDP)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") +  
  labs(
    title = "The value of GDP over years",
    x = "Year",
    y = "GDP"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "GDP Growth Annual" = ggplot(data = naomit4, aes(x = year, y = GDP_growth_annual)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") +  
  labs(
    title = "The GDP annual growth over years",
    x = "Year",
    y = "GDP Annual Growth (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "red"),
  "central Government Debt" = ggplot(data = sey_df, aes(x = year, y = central_government_debt_billions)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "pink") +
  labs(
    title = "The annual changes in the central government debt (billions)",
    x = "Year",
    y = "Central Government Debt (billions)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
  "Total Tax Revenue" = ggplot(data = sey_df, aes(x = year, y = total_tax_revenue)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "pink") +
  labs(
    title = "The annual changes in the total tax revenue",
    x = "Year",
    y = "Total Tax Revenue"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Consumer Price Index" = ggplot(data = sey_df, aes(x = year, y = Consumer_price_index)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "pink") +  
  labs(
    title = "The changes in the level of inflation over years",
    x = "Year",
    y = "Consumer Price Index"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Export Value Index" = ggplot(data = Seychelles, aes(x = year, y = export_value_index)) +
  geom_line(aes(group = 1), color = "purple") + 
  geom_point(aes(color = "pink")) +
  labs(
    title = "The annual changes in the export value index (2015=100)",
    x = "Year",
    y = "Export Value Index"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Import Value Index" = ggplot(data = Seychelles, aes(x = year, y = import_value_index)) +
  geom_line(aes(group = 1), color = "purple") + 
  geom_point(aes(color = "pink")) +
  labs(
    title = "The annual changes in the import value index (2015=100)",
    x = "Year",
    y = "Import Value Index"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Exports of Goods and Services" = ggplot(data = sey_df, aes(x = year, y = exports_of_goods_and_services)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "lightblue") +  
  labs(
    title = "The annual changes in the exports of goods and services",
    x = "Year",
    y = "Exports of Goods and Services"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Imports of Goods and Services" = ggplot(data = sey_df, aes(x = year, y = imports_of_goods_and_services)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the imports of goods and services",
    x = "Year",
    y = "Imports of Goods and Services"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
  "Foreign Direct Investment (% of GDP)" = ggplot(data = sey_df, aes(x = year, y = foreign_direct_investment_percentage_of_GDP)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "pink") +
  labs(
    title = "The annual changes in the foreign direct investment (% of GDP)",
    x = "Year",
    y = "Foreign Direct Investment (% of GDP)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))
      )
    } else if (section == "Society and Environment") {
      switch(
        plot_selector,
        "CO2 Emissions" = ggplot(data = sey_df, aes(x = year, y = CO2_emissions_kt)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the CO2 emissions(kt)",
    x = "Year",
    y = "CO2 Emissions (kt)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Renewable Energy Consumption Proportion"= ggplot(data = sey_df, aes(x = year, y = renewable_energy_consumption_proportion)) +
  geom_line(aes(group = 1), color = "purple") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the renewable energy consumption proportion",
    x = "Year",
    y = "Proportion (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Individuals Access to Electricity Proportion" = ggplot(data = sey_df, aes(x = year, y = access_to_electricity_proportion)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the access-to-electricity population proportion",
    x = "Year",
    y = "Proportion (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Individuals Using the Internet Proportion" = ggplot(data = sey_df, aes(x = year, y = individuals_using_the_Internet_proportion)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the individuals using the Internet proportion",
    x = "Year",
    y = "Proportion (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Young Percentage of Working Age Population" = ggplot(data = sey_df, aes(x = year, y = young_percentage_of_working_age_popu)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "lightblue") + 
  labs(
    title = "The annual changes in the proportion of young laborers within the total labor force",
    x = "Year",
    y = "Proportion of Young Laborers (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Old Percentage of Working Age Population" = ggplot(data = sey_df, aes(x = year, y = old_percentage_of_working_age_popu)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "lightblue") + 
  labs(
    title = "The annual changes in the proportion of old laborers within the total labor force",
    x = "Year",
    y = "Proportion of Old Laborers (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5)),
        "Unemployment Proportion" = ggplot(data = sey_df, aes(x = year, y = unemployment_prop)) +
  geom_line(aes(group = 1), color = "blue") +
  geom_point(color = "lightblue") +
  labs(
    title = "The annual changes in the proportion of unemployment population",
    x = "Year",
    y = "Proportion of Unemployment Population (%)"
  ) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9)) +
  scale_x_continuous(breaks = seq(1960, 2022, by = 5))
      )
    }
  })

  output$selected_plot <- renderPlot({
    print(selected_plot())
  })
  output$country_comparison_table <- renderTable({

    country_comparison_data <- data.frame(
      Aspect = c("Geographical Location", "Area (sq km)", "Population", "Population Density", "GDP (USD)", "GDP per Capita (USD)", 
                 "Main Economic Sectors", "Government Type", "Capital", "Capital Longitude", "Capital Latitude", "Average Age", 
                 "Male-Female Ratio", "Language", "Climate", "Average Temperature (C)", "Average Precipitation (mm)", 
                 "International Trade", "Inflation Rate", "Environmental Pollution", "Unemployment Rate", "Crime Rate"),
      Seychelles = c("Indian Ocean West", 459, 98823, 215, 1.754e9, 17700, "Services, Tourism", "Republic", "Victoria", 55.45, -4.62, 33, 0.96, "Seychellois Creole, English, French", "Tropical", 27.5, 2100, "Tourism, Fishing", 2.5, "Low", 4.2, 20.5),
      Comoros = c("Northeast Africa", 2034, 896000, 440, 1.219e9, 1360, "Agriculture, Fishing, Services", "Federal Republic", "Moroni", 43.26, -11.69, 19, 1.02, "Comorian, Arabic, French", "Tropical", 26.7, 1000, "Agriculture, Fishing", 1.8, "Moderate", 8.81, 7.6),
      Mauritius = c("Indian Ocean West", 2040, 1268315, 623, 2.748e9, 21660, "Services, Industry, Agriculture", "Democracy", "Port Louis", 57.49, -20.09, 37, 1.02, "English, French, Creole", "Tropical", 23.6, 1200, "Textiles, Sugar, Tourism", 3.5, "Moderate", 6.9, 15.6),
      Reunion = c("Indian Ocean West", 2512, 859959, 343, 2.082e7, 27793, "Agriculture, Fishing, Tourism", "Metropolitan France", "Saint-Denis", 55.47, -20.87, 34.1, 1.07, "French", "Tropical", 24.5, 1541, "Sugar, Rum, Handicrafts, Flower oil extraction", 1.44, "Moderate", 29.68, 17.9)
    )
    return(country_comparison_data)
    
    
  }, rownames = FALSE)
  
  output$Seychelles_visit <- renderTable({
  Seychelles_visit <- data.frame(
    Tips = c("multi-ethnics", 
               "Languages", 
               "Airport", 
               "Climate",
             "Best Time to Visit",
             "Popular Destinations",
             "Popular Add-ons"),
    Content = c("The multi-ethnic roots of the Seychelles people stretch far and wide, including France, India, the UK, China, the Arab world, and other parts of Africa.",
                    "There are three official languages in the Seychelles: Creole, English, and French. The most common language spoken by the Seychellois population is their own Creole variant, Seychellois Creole, or Seselwa. ",
                "All international flights arrive at Seychelles International Airport (SEZ), 8km/5mi south of Victoria on Mahé.",
                    "Seychelles has a tropical climate with high humidity. Temperatures don’t fluctuate much throughout the year. Afternoons are around 30°C/86°F and nights are cooler at around 24°C/75°F. Dry Season: May to September, and Wet Season: October to April.",
                    "March, April, October and November are recommended. (less windy, not too busy)",
                "Main islands: (1) Mahé for experiencing the hustle and bustle of Victoria, walking in Morne Seychellois National Park and some beach time at Beau Vallon; (2) Praslin for seeing coco de mer palms at Vallée de Mai, snorkeling at Ile Cocos and sunbathing on Anse Lazio; (3) La Digue for spending time on picture-perfect beaches Anse Source d’Argent and Grand Anse.",
                "(1) Bird Island for seeing colonies of sooty terns and nesting turtles; (2) Cousin Island for spotting Seychelles warblers and other endemic birds; (3) Curieuse Island for walking along coastal trails and seeing giant tortoises."
    )
  )

  return(Seychelles_visit)
}, rownames = FALSE)
  
  output$swot_table <- renderTable({
  swot_data <- data.frame(
    SWOT = c("Strength", 
               "Weaknesses", 
               "Opportunities", 
               "Threats"),
    Description = c("(1) Thriving Tourism Industry: The scenery is beautiful, with exotic charm and natural landscapes that captivate people.   (2) High Economic Freedom: has a relatively open market economy, being friendly to foreign investments, promoting economic growth.  (3) Political Stability: The country has maintained political and social stability over the years, providing favorable conditions for development.   (4) Cultural Richness: The cultural heritage of Seychelles, influenced by African, European, and Asian traditions, contributes to a vibrant and diverse society.",
                    "(1) Dependency on Imported Energy: largely depends on imported fossil fuels for energy, making it susceptible to price fluctuations in the global energy market.  (2) Inconvenient Transportation: The geographical nature of being an island nation results in relatively inconvenient transportation, posing challenges to trade and logistics.   (3) Limited Resources: Despite abundant natural resources, the small land area of Seychelles imposes restrictions on resource utilization.",
                    "(1) Promotion of Technological Innovation: Investing in technology and innovation can enhance other sectors of the economy, reducing dependence on traditional industries.   (2) Marine Resource Utilization: Seychelles can explore sustainable ways to utilize its vast marine resources, such as fisheries and aquaculture.   (3) Sustainable Development: Seychelles can enhance its attractiveness by promoting sustainable tourism and environmental initiatives.   (4) Marine Resource Utilization: Seychelles can explore sustainable ways to utilize its vast marine resources, such as fisheries and aquaculture.",
                    "(1) Global Competitiveness: Increasing competition in the global tourism market may impact Seychelles' market share and revenue.  (2) Global Economic Uncertainty: Fluctuations and uncertainties in the global economy may adversely affect Seychelles' tourism industry and international trade.  (3) Impact of Climate Change: Climate change may result in rising sea levels and natural disasters, posing a threat to Seychelles' island ecosystems and economy.   (4) Geopolitical Risks: Tensions in geopolitics could negatively impact the security and stability of the region."
    )
  )

  return(swot_data)
}, rownames = FALSE)
  
  output$references_table <- renderTable({
  references_data <- data.frame(
    DataOrigin = c("UN data", "World Bank data (finances)", "IMF data", "Seychelles Meteorological Authority", "Seychelles Climate | Weather & When to Go", "National Bureau of Statistics Seychelles"),  
    Link = c("https://data.un.org/", "https://data.worldbank.org/", "https://www.imf.org/en/Data", "https://www.meteo.gov.sc/#/", "https://www.seyvillas.com/en/guide/at-a-glance/climate", "https://www.nbs.gov.sc/")  
  ) 

  references_data$Link <- sprintf('<a href="%s" target="_blank">%s</a>', references_data$Link, references_data$Link)

  references_data
}, sanitize.text.function = function(x) x, escape = FALSE, rownames = FALSE)



  output$data_origin_note <- renderPrint({
    cat("In the process of creating this shiny app, I would like to express gratitude not only to the aforementioned data references and the  Professor Haviland's course but also to the book 'R for Data Science' and Aidan's help.")
  })
  
  
}

shinyApp(ui, server)

```







